### 2021-04-17 manuscript.rmd
Adding WC; edit bib; ready for DJ
Rename 03 to 030 for better listing

author: 
  - name          : "Chung-hong Chan"
    affiliation   : "1"
    corresponding : yes
    address       : "A5, 6 (section A), 68159 Mannheim, Germany"
    email         : "chung-hong.chan@mzes.uni-mannheim.de"
  - name          : "Adrian Rauschfleisch"
    affiliation   : "2"

affiliation:
  - id            : "1"
    institution   : "Mannheimer Zentrum für Europäische Sozialforschung, Universität Mannheim, Germany"
  - id            : "2"
    institution   : "National Taiwan University, Taiwan"

authornote: |
  The authors would like to thank professor Kasper Welbers (Vrije Universiteit Amsterdam) for his advice on the development of the Dutch dictionary; Dr Junior Yuner Zhu (City University of Hong Kong) for sharing details about her study.
  Source code and data are available at (redacted). Prereg: https://osf.io/2h4w8/

@@

keywords          : "Bayesian inference, multilevel model, comparative communication research, ecological effect"
wordcount         : "0"

>>>>

author: 
  - name          : "(redacted)"
    affiliation   : "1"
    corresponding : yes

affiliation:
  - id            : "1"
    institution   : "Planet dust"

authornote: |
  (redacted).
  Source code and data are available at (redacted). Prereg: https://osf.io/2h4w8/

@@

keywords          : "Bayesian inference, multilevel model, comparative communication research, ecological effect"
wordcount         : "7509"
